---
title: "Detecting Twitter Trolls"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Progress since 10/4
1. Focused on tweets instead of users, since it's hard to collect all the data for a user.

2. Found 3 words lists: swear words <http://www.noswearing.com/dictionary>, insulting words <http://onlineslangdictionary.com/thesaurus/words+meaning+insults+(list+of).html>, bad words <https://www.cs.cmu.edu/~biglou/resources/bad-words.txt>. I combined 3 lists and remove repetitions.

3. Downloaded tweets that are potentially related to Piit-Jolie divorce.

4. Matched each tweet with the combined bad words list. The tweets with >98 percentile number of matched are considered trolls.

```{r}
library(RCurl)
library(twitteR)
library(readr)
library(rvest)
library(dplyr)
library(stringr)

load('raw_data/oct_10_tweets_swear.RData')
swear = read.table('raw_data/swearwords_clean.txt',
                   stringsAsFactors = FALSE)[,1]
insult = read.table('raw_data/insultwords.txt',
                    stringsAsFactors = FALSE)[,1]
bad = read.table('raw_data/bad_words.txt',
                 stringsAsFactors = FALSE)[,1]
negwords = c(swear, insult, bad)
negwords = unique(tolower(negwords))


load('raw_data/oct_9_pitt_tweets.RData')
load('raw_data/oct_9_aniston_tweets.RData')
load('raw_data/oct_9_jolie_tweets.RData')
load('raw_data/oct_9_pitt_divorce_tweets.RData')
load('raw_data/oct_9_jolie_divorce_tweets.RData')
load('raw_data/oct_9_pitt_jolie_tweets.RData')

all.tweets = list(Pitt = tweets.pitt, 
                  Jolie = tweets.jolie, 
                  Aniston = tweets.aniston,
                  Pitt_divorce = tweets.pitt.divorce,
                  Jolie_divorce = tweets.jolie.divorce,
                  Pitt_Jolie = tweets.pitt.jolie)
swear.num = list()
par(mfrow = c(2,3))
for (keyword in names(all.tweets)){
    tweetslist = all.tweets[[keyword]]
    swear.num[[keyword]]  = vector(length = length(tweetslist))
    for (i in 1:length(tweetslist)){
        tweet = tweetslist[[i]]
        text = gsub("[^a-zA-Z0-9 ]", '', tweet@.xData$text)
        swear.num[[keyword]][i] = sum(sapply(1:length(negwords), function(x) length(grep(tolower(negwords[x]), tolower(text)))>=1))
    }
    thr = quantile(swear.num[[keyword]], 0.98)
    hist(swear.num[[keyword]], xlab = 'Number of matched words', main = keyword)
    abline(v = thr, col = 2)
}
```

Print identified trolls
```{r, print_troll}
for (keyword in names(all.tweets)){
    tweetslist = all.tweets[[keyword]]
    print(paste0('TWEETS ABOUT ', keyword))
    for (i in 1:length(tweetslist)){
        if (swear.num[[keyword]][i] >= thr){
            print(tweetslist[[i]])
        }
    }
}
```

## Problems
1. Some matched tweets are not trolls but highly critical.

2. Hard to detect the trolls with no swear words.

3. Whether a tweet is a troll depends on the link it points to.

## Next step of troll identification
1. Find a list of known trolls and a list of random tweets. Add to the dictionary the words of significantly different frequencies between two list (most known troll lists are in images instead of text).

2. From the identified trolls, collect the words that have different frequencies with the list of random tweets and add to the dictionary.

3. Open the link in a tweet and grab key words from the title.

## Troll classification.
Existing dictionary consists of different parts. May classify a troll based on word frequencies in different parts.

<!-- 2. Potential strategy: based on each category in my definition of trolls, search for tweets that match such patterns. Create a dictionary by collecting words from the troll tweets. Then match other tweets with the dictionary. -->
<!-- 3. How should we identify the tweets that contain no rude words but are trolls in nature. -->
<!-- 4. One potential solution: we can match swear words list, sarcastic words list, and do sentiment analysis and pick the words that have negative sentiment. -->
<!-- 5. Find a collection of known trolls, compare the word frequencies with random tweets, pick the ones with significant differences. -->

<!-- ```{r cars} -->
<!-- summary(cars) -->
<!-- ``` -->


